DraftOne

### 2017-03-20 writing/DraftOne.Rmd
Attempt at power_calc using purrr in Draft1 - not working :(

>>>>

##2nd attempt at power_calc

```{r}
power_calc <- function(varying, values, n_reps, n=NULL, central, sd, exposure_type,
                       exposure_trend, exposure_amp, average_outcome, outcome_trend,
                        outcome_amp, rr=NULL, start.date = "2000-01-01",
                        cust_exp_func = NULL, cust_exp_args = NULL,
                        cust_base_func = NULL, cust_lambda_func = NULL,
                        cust_base_args = NULL, cust_lambda_args = NULL, 
                       model, df_year=7){
  if(varying == "n"){
    rep_df <- n %>% map(create_sims, n_reps=n_reps, central=central, sd=sd, 
                        exposure_type = exposure_type,
                        exposure_trend=exposure_trend,exposure_amp=exposure_amp,
                        average_outcome=average_outcome,outcome_trend=outcome_trend,
                        outcome_amp = outcome_amp, rr=rr, start.date = start.date)
      fits <- rep_df %>% map(fit_mods, model=model)
      power <- fits %>% map(power_beta) #makes a list, want to extract the values of power and put in a data frame with values of n.
    }
  else if(varying == "rr"){
    rep_df <- rr %>% map(create_sims, n=n, n_reps=n_reps, central=central, sd=sd, 
                        exposure_type = exposure_type,
                        exposure_trend=exposure_trend,exposure_amp=exposure_amp,
                        average_outcome=average_outcome,outcome_trend=outcome_trend,
                        outcome_amp = outcome_amp, start.date = start.date)
      fits <- rep_df %>% map(fit_mods, model=model)
      power <- fits %>% map(power_beta) #makes a list, want to extract the values of power and put in a data frame with values of rr.
    }
  if(plot == TRUE){
    my_plot <- ggplot2::ggplot(out, ggplot2::aes_(x = ~ x, y = ~ power)) +
      ggplot2::geom_line() + ggplot2::theme_minimal() +
      ggplot2::xlab(varying)
    print(my_plot)
  }
  return(power)
}

#Example that doesn't work: 
power_calc(varying = "n", values = c(5, 10, 25), n_reps = 3, central = 100, sd=10, exposure_type = "continuous", exposure_trend = "cos1", exposure_amp = .6, average_outcome=22, outcome_trend = "no trend", outcome_amp = .6, rr=1.1, start.date = "2000-01-01")
```
